Red, Blue, or Purple? 2024’s Battleground States Tell a Story

### 2024-10-31 paper/paper.qmd

outcome_variables %>%
  kable(
    col.names = c("Variable"),
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))
```

@@

>>>>

outcome_variables %>%
  kable(
    col.names = c("Outcome Variable"),
    caption = "Outcome Variables", 
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))
```

@@

```{r}
#| label: tbl-predictor_variables
#| echo: false
#| eval: true
#| warning: false
#| message: false

# Define the variable names
predictor_variables <- data.frame(
  Variable = c("State", "Pollster", "Candidate Name", "Percentage (pct)", "Sample Size", "Days to Election")
)

# Create the table
predictor_variables %>%
  kable(
    col.names = c("Predictor Variable"),
    caption = "Predictor Variables",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))
```
